### 2017-03-19 paper/paper.tex
Wrote more on schulze implementation
Found minted!

\lstinputlisting[language=JavaScript]{code/candidateNode.ts}

@@

\begin{table}[H]
\centering
\begin{tabular}{l|c|c|c|c|c|}
\cline{2-6}
 & \multicolumn{1}{l|}{A} & \multicolumn{1}{l|}{B} & \multicolumn{1}{l|}{C} & \multicolumn{1}{l|}{D} & \multicolumn{1}{l|}{E} \\ \hline
\multicolumn{1}{|l|}{A} & \cellcolor[HTML]{9B9B9B} & \cellcolor[HTML]{FFDDDD}17 & \cellcolor[HTML]{FFDDDD}14 & \cellcolor[HTML]{DDFFDD}35 & \cellcolor[HTML]{DDFFDD}30 \\ \hline
\multicolumn{1}{|l|}{B} & \cellcolor[HTML]{DDFFDD}33 & \cellcolor[HTML]{9B9B9B} & \cellcolor[HTML]{FFDDDD}24 & \cellcolor[HTML]{DDFFDD}47 & \cellcolor[HTML]{DDFFDD}36 \\ \hline
\multicolumn{1}{|l|}{C} & \cellcolor[HTML]{DDFFDD}36 & \cellcolor[HTML]{DDFFDD}26 & \cellcolor[HTML]{9B9B9B} & \cellcolor[HTML]{DDFFDD}40 & \cellcolor[HTML]{DDFFDD}42 \\ \hline
\multicolumn{1}{|l|}{D} & \cellcolor[HTML]{FFDDDD}15 & \cellcolor[HTML]{FFDDDD}3 & \cellcolor[HTML]{FFDDDD}10 & \cellcolor[HTML]{9B9B9B} & \cellcolor[HTML]{FFDDDD}18 \\ \hline
\multicolumn{1}{|l|}{E} & \cellcolor[HTML]{FFDDDD}20 & \cellcolor[HTML]{FFDDDD}14 & \cellcolor[HTML]{FFDDDD}8 & \cellcolor[HTML]{DDFFDD}32 & \cellcolor[HTML]{9B9B9B} \\ \hline
\end{tabular}
\caption{Pairwise comparison matrix used in the Schulze Mehtod. For example, 17 ballots prefer $A>B$ and 33 ballots prefer $B>A$.}
\label{Pairwise comparison matrix}
\end{table}
\subsubsection{Justification}
The Shulze Method is used by multiple organisations around the world. It has been used by various software organisations such as The Wikimedia Foundation, The Debian Project and Ubuntu. It is also used by political parties such as the Pirate Party in Sweden and various other countries. The process also differs greatly in both method and implementation from the two other voting methods used in this paper.
\subsubsection{Pseudocode}
\label{Schulze psuedocode}
let $d[i,j]$ be the number of ballots that prefer candidate $i$ to candidate $j$\\
let $p[i,j]$ be the strength of the strongest path from candidate $i$ to candidate $j$\\
for $i$ from 1 to $C$\\
\tab for $j$ form 1 to $C$\\
\tab\tab if ($i \ne j$)\\
\tab\tab\tab if ($d[i,j] > d[j,i]$)\\
\tab\tab\tab\tab $p[i,j] \coloneqq d[i,j]$\\
\tab\tab\tab else\\
\tab\tab\tab\tab $p[i,j] \coloneqq 0$\\
\tab\tab\tab endif \\
\tab\tab endif \\
\tab endfor \\
endfor\\
for $i$ from 1 to $C$\\
\tab for $j$ form 1 to $C$\\
\tab\tab if ($i \ne j$)\\
\tab\tab\tab for $k$ from 1 to $C$\\
\tab\tab\tab\tab if ($i \ne k \text{ and } j \ne k$)\\
\tab\tab\tab\tab\tab $p[j,k] \coloneqq \text{max }(p[j,k], \text{ min }(p[j,k], p[i,k]))$\\
\tab\tab\tab\tab endif \\
\tab\tab\tab endfor \\
\tab\tab endif \\
\tab endfor \\
endfor\\

\section{Evaluation of methods}
\subsection{Sample I}
\subsection{Sample II}
\subsection{Sample III}

>>>>

\lstinputlisting[language=JavaScript, label=some-code, caption=Some Code]{code/candidateNode.txt}

@@

\begin{table}[H]
\centering
\begin{tabular}{l|c|c|c|c|c|}
\cline{2-6}
 & \multicolumn{1}{l|}{A} & \multicolumn{1}{l|}{B} & \multicolumn{1}{l|}{C} & \multicolumn{1}{l|}{D} & \multicolumn{1}{l|}{E} \\ \hline
\multicolumn{1}{|l|}{A} & \cellcolor[HTML]{9B9B9B} & \cellcolor[HTML]{FFDDDD}17 & \cellcolor[HTML]{FFDDDD}14 & \cellcolor[HTML]{DDFFDD}35 & \cellcolor[HTML]{DDFFDD}30 \\ \hline
\multicolumn{1}{|l|}{B} & \cellcolor[HTML]{DDFFDD}33 & \cellcolor[HTML]{9B9B9B} & \cellcolor[HTML]{FFDDDD}24 & \cellcolor[HTML]{DDFFDD}47 & \cellcolor[HTML]{DDFFDD}36 \\ \hline
\multicolumn{1}{|l|}{C} & \cellcolor[HTML]{DDFFDD}36 & \cellcolor[HTML]{DDFFDD}26 & \cellcolor[HTML]{9B9B9B} & \cellcolor[HTML]{DDFFDD}40 & \cellcolor[HTML]{DDFFDD}42 \\ \hline
\multicolumn{1}{|l|}{D} & \cellcolor[HTML]{FFDDDD}15 & \cellcolor[HTML]{FFDDDD}3 & \cellcolor[HTML]{FFDDDD}10 & \cellcolor[HTML]{9B9B9B} & \cellcolor[HTML]{FFDDDD}18 \\ \hline
\multicolumn{1}{|l|}{E} & \cellcolor[HTML]{FFDDDD}20 & \cellcolor[HTML]{FFDDDD}14 & \cellcolor[HTML]{FFDDDD}8 & \cellcolor[HTML]{DDFFDD}32 & \cellcolor[HTML]{9B9B9B} \\ \hline
\end{tabular}
\caption{Pairwise comparison matrix used in the Schulze Mehtod. For example, 17 ballots prefer $A>B$ and 33 ballots prefer $B>A$.}
\label{Pairwise comparison matrix}
\end{table}
\subsubsection{Justification}
The Shulze Method is used by multiple organisations around the world. It has been used by various software organisations such as The Wikimedia Foundation, The Debian Project and Ubuntu. It is also used by political parties such as the Pirate Party in Sweden and various other countries. The process also differs greatly in both method and implementation from the two other voting methods used in this paper.
\subsubsection{Pseudocode}
\label{Schulze psuedocode}
let $d[i,j]$ be the number of ballots that prefer candidate $i$ to candidate $j$\\
let $p[i,j]$ be the strength of the strongest path from candidate $i$ to candidate $j$\\
for $i$ from 1 to $C$\\
\tab for $j$ form 1 to $C$\\
\tab\tab if ($i \ne j$)\\
\tab\tab\tab if ($d[i,j] > d[j,i]$)\\
\tab\tab\tab\tab $p[i,j] \coloneqq d[i,j]$\\
\tab\tab\tab else\\
\tab\tab\tab\tab $p[i,j] \coloneqq 0$\\
\tab\tab\tab endif \\
\tab\tab endif \\
\tab endfor \\
endfor\\
for $i$ from 1 to $C$\\
\tab for $j$ form 1 to $C$\\
\tab\tab if ($i \ne j$)\\
\tab\tab\tab for $k$ from 1 to $C$\\
\tab\tab\tab\tab if ($i \ne k \text{ and } j \ne k$)\\
\tab\tab\tab\tab\tab $p[j,k] \coloneqq \text{max }(p[j,k], \text{ min }(p[j,k], p[i,k]))$\\
\tab\tab\tab\tab endif \\
\tab\tab\tab endfor \\
\tab\tab endif \\
\tab endfor \\
endfor\\
\subsubsection{Implementation}
The Shulze Method is implemented within the file \texttt{schulze/index.ts}. It takes two inputs: a list of ballots and the number of seats to be elected. A ballot is an ordered list of candidates. The output of the program is a list of winners.
\section{Evaluation of methods}
\subsection{Sample I}
\subsection{Sample II}
\subsection{Sample III}
